---
title: "Tests"
author: "Jordan Eissner"
date: "March 28, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Tests for Cloud_classification 

```{r cloud_class_source, echo=TRUE}
source("Cloud_classification.R")
```

See if the function is classifying the right clouds

```{r cloud_test, echo=TRUE}
CTH <- c(2600,3750,5500,9050,6000,1550)
CBH <- c(2000,300,2000,250,400,800)

data <- cbind(CTH,CBH)

h <- Cloud_classification(data)$shallow
i <- Cloud_classification(data)$congestus

for (x in h){
if (x > 4000)
{
  print("passed")
} else
{
  print("failed")
}}

for (x in i){
if (x > 5000 && x < 9000)
{
  print("passed")
} else
{
  print("failed")
}}
```

## Tests for Precip_classification

```{r precip_class_source, echo=TRUE}
source("Precip_classification.R")
```
 See if the function is correctly classifying the precipitation and creating the right four regimes. 
 
```{r precip_test, echo=TRUE}
CTH <- c(2600,3750,5500,9050,6000,1550)
CBH <- c(2000,300,2000,250,400,800)

data <- cbind(CTH,CBH)

h <- Precip_classification(data)$shallow_precip
i <- Precip_classification(data)$shallow_noprecip
j <- Precip_classification(data)$congestus_precip
k <- Precip_classification(data)$congestus_noprecip

for (x in h){
if (x < 500)
{
  print("passed")
} else
{
  print("failed")
}}

for (x in i){
if (x > 500)
{
  print("passed")
} else
{
  print("failed")
}}
```
 

## Tests for analysis
```{r analysis_source, echo=TRUE}
source("Analyze.R")
```

### $R^2$
See if the function is correctly calculating $R^2$ values. 

```{r analysis_test, echo=TRUE}

x <- c(1,2,3,4,5)
y <- c(1,2,3,4,5)

R <- Analyze(x,y)

if (R==1)
{
  print("passed")
} else
{
  print("failed")
}
```


### T test
```{r ttest_source, echo=TRUE}
source("T-test.R")
```

See if the function is correctly calculating p-values from the t-test.
```{r ttest_test, echo=TRUE}

x <- c(1,2,3,4,5)
y <- c(1,2,3,4,5)

P <- T_test(x,y)

if (P==1)
{
  print("passed")
} else
{
  print("failed")
}
```
